---
title: "data_collect"
author: "hqxue"
date: "2017.7.28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# µÚÒ»ÕÂ summary

## first install

We need install some packages,like follows:(ps. "eval=FALSE" can stop code run)

```{r eval=FALSE}
install.packages(c("stringr", "XML", "maps"))
```

## second library

After we install them, we need library these packages:(ps."echo=FALSE" can hide its code, "include=FALSE" can hide code and results)

```{r}
library(stringr)
library(XML)
library(maps)
library(httr)
```

## third load the data from html

Now, we can load the data into R.(ps.ctrl+alt+I can add chunks quickly)

* the code from book doesnt work 

```{r eval=FALSE}
heritage_parsed <- htmlParse("http://en.wikipedia.org/wiki/List_of_World_Heritage_in_Danger", encoding = "UTF-8")
tables <- readHTMLTable(heritage_parsed, stringsAsFactors = FALSE)
```

* the code from web works 

```{r}
heritage_parsed <- GET("http://en.wikipedia.org/wiki/List_of_World_Heritage_in_Danger")
tables <- readHTMLTable(rawToChar(heritage_parsed$content))
```

## find the table we need

```{r}
danger_table <- tables[[2]]
names(danger_table)
danger_table <- danger_table[,c(1,3,4,6,7)]
colnames(danger_table) <- c("name","locn","crit","yins","yend")
danger_table$name[1:3]
```

## process data

```{r}
# cleanse criteria
danger_table$crit <- ifelse(str_detect(danger_table$crit, "Natural")==T, "nat", "cult")
danger_table$crit[1:3]
# cleanse years
danger_table$yins <- as.numeric(as.character(danger_table$yins))
danger_table$yins

danger_table$yend <- as.character(danger_table$yend)
yend_clean <- unlist(str_extract_all(danger_table$yend, "[[:digit:]]{4}$"))
danger_table$yend <- as.numeric(yend_clean)
danger_table$locn[c(1,3,5)]

# get countries
reg <- "[[:alpha:] ]+(?=[[:digit:]])"
country <- str_extract(danger_table$locn, perl(reg)) # use forward assertion in Perl regular expression
country
country[29] <- "C??te d'Ivoire / Guinea"
country[32] <- ""
danger_table$country <- country

# get coordinates
reg_y <- "[/][ -]*[[:digit:]]*[.]*[[:digit:]]*[;]"
reg_x <- "[;][ -]*[[:digit:]]*[.]*[[:digit:]]*"
y_coords <- str_extract(danger_table$locn, reg_y)
(y_coords <- as.numeric(str_sub(y_coords, 3, -2)))
danger_table$y_coords <- y_coords
x_coords <- str_extract(danger_table$locn, reg_x)
(x_coords <- as.numeric(str_sub(x_coords, 3, -1)))
danger_table$x_coords <- x_coords
danger_table$locn <- NULL


```







